Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-07-30 prevalence_testing/postshocktest2022draft.tex
small change to discussion of employment

The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.  This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not hope to recover the full shock effect.  However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution (\textcolor{red}{Think about this}).  Instead, what is needed is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics (?).

>>>>

The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.  This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not reasonably hope to recover the full shock effect.  However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution.  What is potentially as important or more important is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics.  It is therefore the latter that may best explain the performance of the decision-making method developed here.
